## Exercise 1

```{r setup, include=FALSE}
#| eval: true
#| echo: false

library(dplyr)
library(tidyverse)
library(ggplot2)
library(patchwork)
```

## Loading the dataset

```{r setup_visible}
#| echo: true

library(tidytuesdayR)

tuesdata <- tidytuesdayR::tt_load('2023-12-05')

life_expectancy <- tuesdata$life_expectancy
life_expectancy_different_ages <- tuesdata$life_expectancy_different_ages
life_expectancy_female_male <- tuesdata$life_expectancy_female_male
```

## Solve the following questions:

1. From `life_expectancy`, find the mean life expectancy of countries for each year. Save the result as `mean_life_exp_year`
2. What type of chart would be suitable to show the mean life expectancy each year? Can you plot that chart for years above 1940? Format the chart appropriately
3. Pick any 3 variables from the `life_expectacny_different_ages` and plot variable(s) you are interested in exploring
4. From `life_expectancy_different_ages`, create dataset `life_exp_ages` that calculates the mean life expectancy of countries for ages 0 and 80 for each year. Plot a line chart that shows the life expectancy of both ages
5. From `life_expectancy`, plot a bar chart that shows the life expectancy of India, China, USA, UK, France, Brazil for the year 2021
6. Plot a graph that shows the trend in difference between mean life expectancy of males and females over the years for United States and India. Combine them to show them side by side
7. Can you replicate the following graph?

<https://twitter.com/jayatisharmaa/status/1733493830702526945>


```{r, include=FALSE}
mean_year <- life_expectancy |>
 group_by(Year) |>
 summarise(mean_life_exp = mean(LifeExpectancy))

mean_year |>
  filter(Year >= 1900) |>
  ggplot(aes(x = Year, y = mean_life_exp)) +
  geom_line()

life_exp_ages <- life_expectancy_different_ages |>
  drop_na() |>
  group_by(Year) |>
  summarise(mean_life_exp_0 = mean(LifeExpectancy0),
            mean_life_exp_10 = mean(LifeExpectancy10))


ggplot(data = life_exp_ages) +
  geom_line(aes(x = Year, y = mean_life_exp_0))+
  geom_line(aes(x = Year, y = mean_life_exp_10))

life_expectancy |>
  filter(Year == 2021 & Entity %in% c("India", "Brazil", "France", "United Kingdom", "China", "United States") ) |>
  ggplot(aes(x = Entity, y = LifeExpectancy))+
  geom_col()

US <- life_expectancy_female_male |>
  filter(Entity == "United States") |>
  ggplot(aes(x = Year, y = LifeExpectancyDiffFM))+
  geom_line()

IND <- life_expectancy_female_male |>
  filter(Entity == "India") |>
  ggplot(aes(x = Year, y = LifeExpectancyDiffFM))+
  geom_line()

US + IND
```

